---
title: "poisson-dist-experiment"
output: pdf_document
---

## What is the shape of distribution when lambda is small in poisson distribution

When lambda is small , we can find that the shape of poisson shift to left.

Let's experiment when lambda is 1, 2, and 4

```{r cars}
pos.sample<- rpois(1000, 0.5)
pos.sample.df <-data.frame(pos.sample)
sampl.agg.df <- aggregate(pos.sample.df$pos.sample, by = list(rv = pos.sample.df$pos.sample) , FUN = sum)
barplot(sampl.agg.df$x~sampl.agg.df$rv, col=c("#ccf0fe9f"), horiz=FALSE, cex.names=0.5, las=1, width=1, 
        xlab="lambda is 0.5", ylab="Frequencies")

pos.sample<- rpois(1000, 1)
pos.sample.df <-data.frame(pos.sample)
sampl.agg.df <- aggregate(pos.sample.df$pos.sample, by = list(rv = pos.sample.df$pos.sample) , FUN = sum)
barplot(sampl.agg.df$x~sampl.agg.df$rv, col=c("#ccf0fe9f"), horiz=FALSE, cex.names=0.5, las=1, width=1, 
        xlab="lambda is 1", ylab="Frequencies")

pos.sample<- rpois(1000, 2)
pos.sample.df <-data.frame(pos.sample)
sampl.agg.df <- aggregate(pos.sample.df$pos.sample, by = list(rv = pos.sample.df$pos.sample) , FUN = sum)
barplot(sampl.agg.df$x~sampl.agg.df$rv, col=c("#ccf0fe9f"), horiz=FALSE, cex.names=0.5, las=1, width=1, 
        xlab="lambda is 2", ylab="Frequencies")
```

## What is the shape of distribution when lambda is big in poisson distribution

We consider lambda is big, the distribution shape is bell curve, which is the same as normal distribution shape.

```{r}
pos.sample<- rpois(1000, 50)
pos.sample.df <-data.frame(pos.sample)
sampl.agg.df <- aggregate(pos.sample.df$pos.sample, by = list(rv = pos.sample.df$pos.sample) , FUN = sum)
barplot(sampl.agg.df$x~sampl.agg.df$rv, col=c("#ccf0fe9f"), horiz=FALSE, cex.names=0.5, las=1, width=1, 
        xlab="lambda is 50", ylab="Frequencies")
```
